New Evidence on the Soft Budget Constraint: Chinese Environmental Policy Effectiveness in Private versus SOEs\thanks{We would like to thank Zhao Ruili and Zhou Ling for their precious help in collecting the data from the China Environment Statistics Yearbook.}

### 2020-02-01 Paper/main.tex

\begin{table}[!htbp] \centering
  \caption{SO2 reduction during the subsequent FYP}
  \begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
    \label{tab:table1}
    \begin{tabular}{lrrrr}
      \toprule
      {} & \multicolumn{2}{l}{Failure} & \multicolumn{1}{l}{Success} \\
      \hline
      &      (1998-2000) & (2001-2005) &  (2006-2010) \\
      \midrule
      \textbf{TCZ} & & & \\
      \text{\footnotesize{SO2 target}}       & -     & -     & -14\% &   \\
      \text{\footnotesize{SO2 \% reduction}} & -7\% & 38\%  & -15\%     &   \\

@@

\begin{table}[!htbp] \centering
    \caption{ Summary Statistics by city-industry and city characteristics}
      \begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
    \label{tab:table2}
    \begin{tabular}{lrrrr}
      \multicolumn{1}{l}{\textbf{\small Panel A: City/city-industry}} \\
      \toprule
      & \multicolumn{2}{c}{No TCZ} & \multicolumn{2}{c}{TCZ} \\
      & \multicolumn{1}{c}{mean} & \multicolumn{1}{c}{std} & \multicolumn{1}{c}{mean} & \multicolumn{1}{c}{std}\\
      %{}                         & mean   & std    & mean   & std    \\
      \midrule
      $SO2_{ikt}$                  & 182,873 & 372,028 & 174,308 & 357,225 \\
      $\text{count share SOE}_k$   & 0.093  & 0.094  & 0.082  & 0.086  \\
      $\text{output share SOE}_k$  & 0.147  & 0.153  & 0.136  & 0.151  \\
      $\text{capital share SOE}_k$ & 0.220  & 0.197  & 0.209  & 0.198  \\
      $\text{labour share SOE}_k$  & 0.188  & 0.162  & 0.176  & 0.162  \\
      $\text{output}_{kit}$        & 0.028  & 0.101  & 0.058  & 0.266  \\
      $\text{capital}_{kit}$       & 0.008  & 0.030  & 0.014  & 0.054  \\
      $\text{labour}_{kit}$        & 0.009  & 0.024  & 0.016  & 0.056  \\
      \bottomrule
      \\ %%% Create second table
      \multicolumn{1}{l}{\textbf{\small Panel B: SO2 emission by city-location}} \\
      \toprule
      {} & \multicolumn{2}{l}{\footnotesize difference (10.000 tons units)} & \multicolumn{2}{l}{variance (\footnotesize \%)} \\
      %& \multicolumn{1}{l}{No TCZ} & \multicolumn{1}{l}{TCZ} & %\multicolumn{1}{l}{No TCZ} & \multicolumn{1}{l}{TCZ}\\
                  & No TCZ   & TCZ      & No TCZ & TCZ  \\
      Location    &          &          &        &      \\
      \midrule
      Full sample &    -192 & -436 &     0.22 & 0.26 \\
      Central     &    -238 & -232 &     0.25 & 0.19 \\
      Coastal     &    -138 & -659 &     0.12 & 0.29 \\
      Northeast   &    -206 &  -89 &     0.30 & 0.08 \\
      Northwest   &    -115 & -277 &     0.21 & 0.31 \\
      Southwest   &    -272 & -503 &     0.31 & 0.29 \\
      Non Coastal &    -215 & -302 &     0.28 & 0.23 \\
      Coastal     &    -140 & -578 &     0.13 & 0.28 \\
      \bottomrule
      \hline
    \end{tabular}
    \end{adjustbox}
    \begin{tablenotes}
      \small
      \item 
      Sources: Author's own computation \\
      Panel A provides summary statistics for the main variables used in the subsequent empirical analysis. \\
  Panel B provides summary statistics for the SO2 emission (in 10.000 tons) for Chinese cities (228), split into TCZ (140) and non-TCZ (88) cities
      \\
    \end{tablenotes}
\end{table}

@@

\begin{equation} \label{eq:paralleltrend}
\begin{aligned} 
\text {Log SO2 emission }_{i k t}=\sum_{t=2002}^{2007} \alpha (T C Z_{i}  \times \text {  Polluting sectors }_{k} \times year _{t}) + \\ 
\theta {X}_{i k t}+\nu_{ik}+\lambda_{it} +\phi_{kt} +\epsilon_{ikt} 
\end{aligned}
\end{equation}
In which $year_t$ is a dummy set equal to one with $t$ ranging from the year 2002 to 2007.

\begin{table}[!htb] \centering
  \caption{Parallel trend}
  \begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
    \label{tab:table4}
    \begin{tabular}{@{\extracolsep{5pt}}lccc}
      \\[-1.8ex]\hline
      \hline \\[-1.8ex]
      & \multicolumn{3}{c}{The Dependent variable: $\text{Ln SO2}_{ikt}$} \\
      \cline{2-4}
      \\[-1.8ex] & (1) & (2) & (3)\\
      \\[-1.8ex] & (All sample) & (TCZ) & (No TCZ)\\
      \\[-1.8ex] & $(TCZ_i \times \text{Polluting}_k \times Year)$ & $(Polluting_k \times Year)$ & $(Polluting_k \times Year)$\\
      \hline \\[-1.8ex]
      2003                        & $-$0.409       & $-$0.091       & 0.228   \\
                                  & (0.272)        & (0.115)        & (0.259) \\
      2004                        & $-$0.253       & $-$0.098       & 0.078   \\
                                  & (0.287)        & (0.112)        & (0.308) \\
      2005                        & $-$0.420       & $-$0.153       & 0.178   \\
                                  & (0.263)        & (0.127)        & (0.272) \\
      2006                        & $-$0.503$^{*}$ & $-$0.211       & 0.159   \\
                                  & (0.270)        & (0.129)        & (0.288) \\
      2007                        & $-$0.460       & $-$0.246$^{*}$ & 0.127   \\
                                  & (0.303)        & (0.145)        & (0.312) \\
      \hline \\[-1.8ex]
      City-year fixed effects     & Yes            & Yes            & Yes     \\
      Industry-year fixed effects & Yes            & No             & No      \\
      City-industry fixed effects & Yes            & Yes            & Yes     \\
      Observations                & 30,676         & 23,333         & 7,343   \\
      R$^{2}$                     & 0.851          & 0.827          & 0.861   \\
      \hline
      \hline \\[-1.8ex]
      \end{tabular}
  \end{adjustbox}
  \begin{tablenotes}
      \small
      \item 
      Note: $^{*}$p$<$0.1 $^{**}$p$<$0.05 $^{***}$p$<$0.01 \\
      Heteroskedastiikty-robust standard errors in parentheses are clustered by city \\
    \end{tablenotes}
\end{table}

@@

\begin{table}[!htb] \centering
  %\resizebox{1\textwidth}{!}{
    %\begin{threeparttable}
    \caption{State versus private sectors}
      \begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
     \label{tab:table7}
      \begin{tabular}{lrrrr}
        \multicolumn{1}{l}{\textbf{Panel A: SOE Dominating sectors}} \\
        \toprule
        & \multicolumn{3}{c}{The Dependent variable: $\text{Ln SO2}_{ikt}$} \\
        \cline{2-4}
        \\[-1.8ex] & (1) & (2) & (3) \\
        \\[-1.8ex] & (Output) & (Capital) & (Labour)\\
        \hline \\[-1.8ex]
        $TCZ_i \times \text{Polluting}_k \times \text{Period}$ & 0.101           & 0.114           & 0.235           \\
                                                            & (0.234)         & (0.229)         & (0.232)         \\
        \hline \\[-1.8ex]
        City-year fixed effects                             & Yes             & Yes             & Yes             \\
        Industry-year fixed effects                         & Yes             & Yes             & Yes             \\
        City-industry fixed effects                         & Yes             & Yes             & Yes             \\
        Observations                                        & 9,824           & 10,423          & 10,076          \\
        Number sectors                                      & 92              & 104             & 98              \\
        R$^{2}$                                             & 0.865           & 0.869           & 0.862           \\
        \bottomrule
        \\ %%% Create second table
        \multicolumn{1}{l}{\textbf{Panel B: Prviate Dominating sectors}} \\
        \toprule
        & \multicolumn{3}{c}{The Dependent variable: $Ln SO2_{ikt}$} \\
        \cline{2-4}
        \\[-1.8ex] & (1) & (2) & (3)\\
        \\[-1.8ex] &  (Output)& (Capital) & (Labour) \\
        \hline \\[-1.8ex]
        $TCZ_i \times \text{Polluting}_k \times \text{Period}$ & $-$0.243$^{**}$ & $-$0.272$^{**}$ & $-$0.284$^{**}$ \\
                                                            & (0.124)         & (0.124)         & (0.125)         \\
        \hline \\[-1.8ex]
        City-year fixed effects                             & Yes             & Yes             & Yes             \\
        Industry-year fixed effects                         & Yes             & Yes             & Yes             \\
        City-industry fixed effects                         & Yes             & Yes             & Yes             \\
        Observations                                        & 20,852          & 20,253          & 20,600          \\
        Number sectors                                      & 204             & 192             & 198             \\
        R$^{2}$                                             & 0.857           & 0.853           & 0.858           \\
    \end{tabular}
    \end{adjustbox}
    \begin{tablenotes}
      \small
      \item 
      Note: $^{*}$p$<$0.1 $^{**}$p$<$0.05 $^{***}$p$<$0.01 \\
      Heteroskedastiikty-robust standard errors in parentheses are clustered by city \\
    \end{tablenotes}
\end{table}

@@

\begin{equation} \label{eq:citymandate}
\begin{aligned} 
\text {Log SO2 emission }_{i k t}=& \alpha  (\text { Period }  \times \text{Target}_i \times \text {  Polluting sectors }_{k}) +\nu_{ik}+\lambda_{it} +\phi_{kt} +\epsilon_{ikt}  
\end{aligned}
\end{equation}

>>>>

\begin{table}[!htbp] \centering
  \caption{SO2 reduction during the subsequent FYPs}
  \begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
    \label{tab:table1}
    \begin{tabular}{lrrrr}
      \toprule
      {} & \multicolumn{2}{l}{Failure} & \multicolumn{1}{l}{Success} \\
      \hline
      &      (1998-2000) & (2001-2005) &  (2006-2010) \\
      \midrule
      \textbf{TCZ} & & & \\
      \text{\footnotesize{SO2 target}}       & -     & -     & -14\% &   \\
      \text{\footnotesize{SO2 \% reduction}} & -7\% & 38\%  & -15\%     &   \\

@@

\begin{table}[!htbp] \centering
    \caption{ Summary statistics by city-industry and city characteristics}
      \begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
    \label{tab:table2}
    \begin{tabular}{lrrrr}
      \multicolumn{1}{l}{\textbf{\small Panel A: City/city-industry}} \\
      \toprule
      & \multicolumn{2}{c}{No TCZ} & \multicolumn{2}{c}{TCZ} \\
      & \multicolumn{1}{c}{mean} & \multicolumn{1}{c}{std} & \multicolumn{1}{c}{mean} & \multicolumn{1}{c}{std}\\
      %{}                         & mean   & std    & mean   & std    \\
      \midrule
      $SO2_{ikt}$                  & 182,873 & 372,028 & 174,308 & 357,225 \\
      $\text{count share SOE}_k$   & 0.093  & 0.094  & 0.082  & 0.086  \\
      $\text{output share SOE}_k$  & 0.147  & 0.153  & 0.136  & 0.151  \\
      $\text{capital share SOE}_k$ & 0.220  & 0.197  & 0.209  & 0.198  \\
      $\text{labour share SOE}_k$  & 0.188  & 0.162  & 0.176  & 0.162  \\
      $\text{output}_{kit}$        & 0.028  & 0.101  & 0.058  & 0.266  \\
      $\text{capital}_{kit}$       & 0.008  & 0.030  & 0.014  & 0.054  \\
      $\text{labour}_{kit}$        & 0.009  & 0.024  & 0.016  & 0.056  \\
      \bottomrule
      \\ %%% Create second table
      \multicolumn{1}{l}{\textbf{\small Panel B: SO2 emission by city-location}} \\
      \toprule
      {} & \multicolumn{2}{l}{\footnotesize difference (10.000 tons units)} & \multicolumn{2}{l}{variance (\footnotesize \%)} \\
      %& \multicolumn{1}{l}{No TCZ} & \multicolumn{1}{l}{TCZ} & %\multicolumn{1}{l}{No TCZ} & \multicolumn{1}{l}{TCZ}\\
                  & No TCZ   & TCZ      & No TCZ & TCZ  \\
      Location    &          &          &        &      \\
      \midrule
      Full sample &    -192 & -436 &     0.22 & 0.26 \\
      Central     &    -238 & -232 &     0.25 & 0.19 \\
      Coastal     &    -138 & -659 &     0.12 & 0.29 \\
      Northeast   &    -206 &  -89 &     0.30 & 0.08 \\
      Northwest   &    -115 & -277 &     0.21 & 0.31 \\
      Southwest   &    -272 & -503 &     0.31 & 0.29 \\
      Non Coastal &    -215 & -302 &     0.28 & 0.23 \\
      Coastal     &    -140 & -578 &     0.13 & 0.28 \\
      \bottomrule
      \hline
    \end{tabular}
    \end{adjustbox}
    \begin{tablenotes}
      \small
      \item 
      Sources: Author's own computation \\
      Panel A provides summary statistics for the main variables used in the subsequent empirical analysis. \\
  Panel B provides summary statistics for the SO2 emission (in 10.000 tons) for Chinese cities (228), split into TCZ (140) and non-TCZ (88) cities
      \\
    \end{tablenotes}
\end{table}

@@

\begin{equation} \label{eq:paralleltrend}
\begin{aligned} 
\text {Log SO2 emission }_{i k t}=\sum_{t=2002}^{2007} \alpha (T C Z_{i}  \times \text {  Polluting sectors }_{k} \times year _{t})  \\ 
+ \theta {X}_{i k t}+\nu_{ik}+\lambda_{it} +\phi_{kt} +\epsilon_{ikt} 
\end{aligned}
\end{equation}
In which $year_t$ is a dummy set equal to one with $t$ ranging from the year 2002 to 2007.

\begin{table}[!htb] \centering
  \caption{Parallel trends}
  \begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
    \label{tab:table4}
    \begin{tabular}{@{\extracolsep{5pt}}lccc}
      \\[-1.8ex]\hline
      \hline \\[-1.8ex]
      & \multicolumn{3}{c}{The Dependent variable: $\text{Ln SO2}_{ikt}$} \\
      \cline{2-4}
      \\[-1.8ex] & (1) & (2) & (3)\\
      \\[-1.8ex] & (All sample) & (TCZ) & (No TCZ)\\
      \\[-1.8ex] & $(TCZ_i \times \text{Polluting}_k \times Year)$ & $(Polluting_k \times Year)$ & $(Polluting_k \times Year)$\\
      \hline \\[-1.8ex]
      2003                        & $-$0.409       & $-$0.091       & 0.228   \\
                                  & (0.272)        & (0.115)        & (0.259) \\
      2004                        & $-$0.253       & $-$0.098       & 0.078   \\
                                  & (0.287)        & (0.112)        & (0.308) \\
      2005                        & $-$0.420       & $-$0.153       & 0.178   \\
                                  & (0.263)        & (0.127)        & (0.272) \\
      2006                        & $-$0.503$^{*}$ & $-$0.211       & 0.159   \\
                                  & (0.270)        & (0.129)        & (0.288) \\
      2007                        & $-$0.460       & $-$0.246$^{*}$ & 0.127   \\
                                  & (0.303)        & (0.145)        & (0.312) \\
      \hline \\[-1.8ex]
      City-year fixed effects     & Yes            & Yes            & Yes     \\
      Industry-year fixed effects & Yes            & No             & No      \\
      City-industry fixed effects & Yes            & Yes            & Yes     \\
      Observations                & 30,676         & 23,333         & 7,343   \\
      R$^{2}$                     & 0.851          & 0.827          & 0.861   \\
      \hline
      \hline \\[-1.8ex]
      \end{tabular}
  \end{adjustbox}
  \begin{tablenotes}
      \small
      \item 
      Note: $^{*}$p$<$0.1 $^{**}$p$<$0.05 $^{***}$p$<$0.01 \\
      Heteroskedastiikty-robust standard errors in parentheses are clustered by city \\
    \end{tablenotes}
\end{table}

@@

\begin{table}[!htb] \centering
  %\resizebox{1\textwidth}{!}{
    %\begin{threeparttable}
    \caption{State versus private sectors}
      \begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
     \label{tab:table7}
      \begin{tabular}{lrrrr}
        \multicolumn{1}{l}{\textbf{Panel A: SOE Dominating sectors}} \\
        \toprule
        & \multicolumn{3}{c}{The Dependent variable: $\text{Ln SO2}_{ikt}$} \\
        \cline{2-4}
        \\[-1.8ex] & (1) & (2) & (3) \\
        \\[-1.8ex] & (Output) & (Capital) & (Labour)\\
        \hline \\[-1.8ex]
        $TCZ_i \times \text{Polluting}_k \times \text{Period}$ & 0.101           & 0.114           & 0.235           \\
                                                            & (0.234)         & (0.229)         & (0.232)         \\
        \hline \\[-1.8ex]
        City-year fixed effects                             & Yes             & Yes             & Yes             \\
        Industry-year fixed effects                         & Yes             & Yes             & Yes             \\
        City-industry fixed effects                         & Yes             & Yes             & Yes             \\
        Observations                                        & 9,824           & 10,423          & 10,076          \\
        Number sectors                                      & 92              & 104             & 98              \\
        R$^{2}$                                             & 0.865           & 0.869           & 0.862           \\
        \bottomrule
        \\ %%% Create second table
        \multicolumn{1}{l}{\textbf{Panel B: Private Dominating sectors}} \\
        \toprule
        & \multicolumn{3}{c}{The Dependent variable: $Ln SO2_{ikt}$} \\
        \cline{2-4}
        \\[-1.8ex] & (1) & (2) & (3)\\
        \\[-1.8ex] &  (Output)& (Capital) & (Labour) \\
        \hline \\[-1.8ex]
        $TCZ_i \times \text{Polluting}_k \times \text{Period}$ & $-$0.243$^{**}$ & $-$0.272$^{**}$ & $-$0.284$^{**}$ \\
                                                            & (0.124)         & (0.124)         & (0.125)         \\
        \hline \\[-1.8ex]
        City-year fixed effects                             & Yes             & Yes             & Yes             \\
        Industry-year fixed effects                         & Yes             & Yes             & Yes             \\
        City-industry fixed effects                         & Yes             & Yes             & Yes             \\
        Observations                                        & 20,852          & 20,253          & 20,600          \\
        Number sectors                                      & 204             & 192             & 198             \\
        R$^{2}$                                             & 0.857           & 0.853           & 0.858           \\
    \end{tabular}
    \end{adjustbox}
    \begin{tablenotes}
      \small
      \item 
      Note: $^{*}$p$<$0.1 $^{**}$p$<$0.05 $^{***}$p$<$0.01 \\
      Heteroskedastiikty-robust standard errors in parentheses are clustered by city \\
    \end{tablenotes}
\end{table}

@@

\begin{equation} \label{eq:citymandate}
\begin{aligned} 
\text {Log SO2 emission }_{i k t}=& \alpha  (\text { Period }  \times \text{Target}_i \times \text {  Polluting sectors }_{k}) \\ + \nu_{ik}+\lambda_{it} +\phi_{kt} +\epsilon_{ikt}  
\end{aligned}
\end{equation}
